A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-11 manuscript.Rmd
talk about automate
explain why you need `rerun()`

@@

The `repro` also contains a function that automatically figures out how to reproduce a project with:

@@

This function also recognizes other employed reproducibility tools (like `renv` and `singularity`), but can of course only guess the appropriate way to reproduce a project.

>>>>

The function `automate()` combines `automate_docker()` & `automate_make()`.

@@

Because you probably want to reproduce your own project each time something changes, you will often want to reproduce evertyhting.
The `repro`-package contains a function designed for that purpose:

@@

This function  automatically figures out how to reproduce a project  and also recognizes other employed reproducibility tools (like `renv` and `singularity`), but can of course only guess the appropriate way to reproduce a project.
